A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-04-04 bioc-workflow_march2017.tex
fixed macro conflicts in tex

There are two aspects related to data normalisation that are relevant
to spatial proteomics data processing. The first one focuses on
reducing purely technical variation between channels without affecting
biological variability (i.e. the shape of the quantitatives
profiles). This normalisation will depend on the underlying
quantitative technology and the experimental design, and will not be
addressed in this workflow. The second aspect, and more specific to
spatial proteomics data, is scaling all the organelle-specific
profiles into \st{a} \hl{the} same intensity interval (typically 0 and 1) by, for
example, dividing each intensity by the sum of the intensities for
that quantitative feature. This is not necessary in this example as
the intensities for each replicate have already been re-scaled to 1 in
Proteome Discoverer v1.4 Thermo Fisher. However, if the data require
normalisation, the user can execute the \texttt{normalise} function as
demonstrated in the below code chunk.

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = structure(list(t = numeric(0), : replacement has 0 rows, data has 10}}\begin{alltt}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Mon Mar 26 16:47:45 2018 
## Subset [6725,20][5032,20] Mon Mar 26 16:48:04 2018 
## Removed features with more than 0 NAs: Mon Mar 26 16:48:04 2018 
## Dropped featureData's levels Mon Mar 26 16:48:04 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Mon Mar 26 16:47:45 2018 
## Subset [6725,20][5032,20] Mon Mar 26 16:48:04 2018 
## Removed features with more than 0 NAs: Mon Mar 26 16:48:04 2018 
## Dropped featureData's levels Mon Mar 26 16:48:04 2018 
## Subset [5032,20][5032,20] Tue Apr  3 17:46:47 2018 
## Removed features with more than 0 NAs: Tue Apr  3 17:46:47 2018 
## Dropped featureData's levels Tue Apr  3 17:46:48 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr  3 17:46:49 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Tue Apr  3 17:46:49 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr  3 17:46:49 2018 
## Added markers from  'pdres' marker vector. Tue Apr  3 17:46:50 2018 
##  MSnbase version: 2.5.10
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4333396               0.3051261               0.3870872 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6736435               0.6011995               0.4213771 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4135168               0.5581414               0.9497578 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7956060               0.7091274               0.3126237 
##         Plasma membrane              Proteasome 
##               0.7100209               0.4188587
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4333396               0.3051261               0.3870872 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6736435               0.6011995               0.4213771 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4135168               0.5581414               0.9497578 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7956060               0.7091274               0.3126237 
##         Plasma membrane              Proteasome 
##               0.7100209               0.4188587
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     172                      89 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     294                     476                     103 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     120                     522 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     316                     158                    2058
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

##  [1] pRolocdata_1.17.2    gridExtra_2.3        xtable_1.8-2        
##  [4] BiocStyle_2.7.8      knitr_1.20           pRoloc_1.19.3       
##  [7] MLInterfaces_1.59.1  cluster_2.0.6        annotate_1.57.2     
## [10] XML_3.98-1.10        AnnotationDbi_1.41.4 IRanges_2.13.28     
## [13] S4Vectors_0.17.37    MSnbase_2.5.10       ProtGenerics_1.11.0 
## [16] BiocParallel_1.13.1  mzR_2.13.5           Rcpp_0.12.16        
## [19] Biobase_2.39.2       BiocGenerics_0.25.3 

@@

##  [13] viridis_0.5.0         gdata_2.18.0          magrittr_1.5         
##  [16] memoise_1.1.0         doParallel_1.0.11     sfsmisc_1.1-2        
##  [19] limma_3.35.13         recipes_0.1.2         gower_0.1.2          
##  [22] rda_1.0.2-2           dimRed_0.1.0          lpSolve_5.6.13       
##  [25] prettyunits_1.0.2     colorspace_1.3-2      blob_1.1.0           
##  [28] dplyr_0.7.4           RCurl_1.95-4.10       hexbin_1.27.2        
##  [31] genefilter_1.61.1     bindr_0.1.1           impute_1.53.0        
##  [34] survival_2.41-3       iterators_1.0.9       glue_1.2.0           
##  [37] DRR_0.0.3             gtable_0.2.0          ipred_0.9-6          
##  [40] zlibbioc_1.25.0       kernlab_0.9-25        ddalpha_1.3.1.1      
##  [43] prabclus_2.2-6        DEoptimR_1.0-8        scales_0.5.0         
##  [46] vsn_3.47.1            mvtnorm_1.0-7         DBI_0.8              
##  [49] viridisLite_0.3.0     progress_1.1.2        foreign_0.8-70       
##  [52] bit_1.1-12            proxy_0.4-21          mclust_5.4           
##  [55] preprocessCore_1.41.0 lava_1.6              prodlim_1.6.1        
##  [58] sampling_2.8          htmlwidgets_1.0       httr_1.3.1           
##  [61] threejs_0.3.1         FNN_1.1               RColorBrewer_1.1-2   
##  [64] fpc_2.1-11            modeltools_0.2-21     pkgconfig_2.0.1      
##  [67] flexmix_2.3-14        nnet_7.3-12           caret_6.0-78         
##  [70] tidyselect_0.2.4      rlang_0.2.0           reshape2_1.4.3       
##  [73] munsell_0.4.3         mlbench_2.1-1         tools_3.5.0          
##  [76] RSQLite_2.0           pls_2.6-0             broom_0.4.3          
##  [79] evaluate_0.10.1       stringr_1.3.0         yaml_2.1.18          
##  [82] mzID_1.17.0           ModelMetrics_1.1.0    bit64_0.9-7          
##  [85] robustbase_0.92-8     randomForest_4.6-12   purrr_0.2.4          
##  [88] dendextend_1.7.0      bindrcpp_0.2          nlme_3.1-136         
##  [91] whisker_0.3-2         mime_0.5              RcppRoll_0.2.2       
##  [94] biomaRt_2.35.12       compiler_3.5.0        e1071_1.6-8          
##  [97] affyio_1.49.1         tibble_1.4.2          stringi_1.1.7        
## [100] highr_0.6             lattice_0.20-35       trimcluster_0.1-2    
## [103] Matrix_1.2-12         psych_1.7.8           gbm_2.1.3            
## [106] pillar_1.2.1          MALDIquant_1.17       bitops_1.0-6         
## [109] httpuv_1.3.6.2        R6_2.2.2              pcaMethods_1.71.0    
## [112] affy_1.57.0           hwriter_1.3.2         codetools_0.2-15     
## [115] MASS_7.3-49           gtools_3.5.0          assertthat_0.2.0     
## [118] CVST_0.2-1            rprojroot_1.3-2       withr_2.1.2          
## [121] mnormt_1.5-5          diptest_0.75-7        grid_3.5.0           
## [124] rpart_4.1-13          timeDate_3043.102     tidyr_0.8.0          
## [127] class_7.3-14          rmarkdown_1.9         shiny_1.0.5          
## [130] lubridate_1.7.3       base64enc_0.1-3

>>>>

There are two aspects related to data normalisation that are relevant
to spatial proteomics data processing. The first one focuses on
reducing purely technical variation between channels without affecting
biological variability (i.e. the shape of the quantitatives
profiles). This normalisation will depend on the underlying
quantitative technology and the experimental design, and will not be
addressed in this workflow. The second aspect, and more specific to
spatial proteomics data, is scaling all the organelle-specific
profiles into \st{a}\hl{the} same intensity interval (typically 0 and 1) by, for
example, dividing each intensity by the sum of the intensities for
that quantitative feature. This is not necessary in this example as
the intensities for each replicate have already been re-scaled to 1 in
Proteome Discoverer v1.4 Thermo Fisher. However, if the data require
normalisation, the user can execute the \texttt{normalise} function as
demonstrated in the below code chunk.

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = structure(list(t = numeric(0), : replacement has 0 rows, data has 10}}\begin{alltt}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Wed Apr  4 13:30:04 2018 
## Subset [6725,20][5032,20] Wed Apr  4 13:30:17 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:30:17 2018 
## Dropped featureData's levels Wed Apr  4 13:30:17 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:33:06 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:33:06 2018 
## Dropped featureData's levels Wed Apr  4 13:33:06 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:42:10 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:42:10 2018 
## Dropped featureData's levels Wed Apr  4 13:42:10 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:45:12 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:45:12 2018 
## Dropped featureData's levels Wed Apr  4 13:45:12 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Wed Apr  4 13:30:04 2018 
## Subset [6725,20][5032,20] Wed Apr  4 13:30:17 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:30:17 2018 
## Dropped featureData's levels Wed Apr  4 13:30:17 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:33:06 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:33:06 2018 
## Dropped featureData's levels Wed Apr  4 13:33:06 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:42:10 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:42:10 2018 
## Dropped featureData's levels Wed Apr  4 13:42:10 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:45:12 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:45:12 2018 
## Dropped featureData's levels Wed Apr  4 13:45:12 2018 
## Subset [5032,20][5032,20] Wed Apr  4 13:47:14 2018 
## Removed features with more than 0 NAs: Wed Apr  4 13:47:14 2018 
## Dropped featureData's levels Wed Apr  4 13:47:14 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Wed Apr  4 13:47:16 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Wed Apr  4 13:47:16 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Wed Apr  4 13:47:15 2018 
## Added markers from  'pdres' marker vector. Wed Apr  4 13:47:17 2018 
##  MSnbase version: 2.5.10
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4369121               0.3042575               0.3807524 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6850502               0.6093775               0.4324733 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4261633               0.5908828               0.9491150 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7944096               0.7083224               0.3140141 
##         Plasma membrane              Proteasome 
##               0.7126035               0.4150477
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4369121               0.3042575               0.3807524 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6850502               0.6093775               0.4324733 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4261633               0.5908828               0.9491150 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7944096               0.7083224               0.3140141 
##         Plasma membrane              Proteasome 
##               0.7126035               0.4150477
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      84                     173                      84 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     297                     468                     102 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      28                     124                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     343                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     322                     159                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

##  [1] BiocStyle_2.7.8      gridExtra_2.3        shiny_1.0.5         
##  [4] pRolocGUI_1.13.1     rgl_0.99.9           pRolocdata_1.17.2   
##  [7] pRoloc_1.19.3        MLInterfaces_1.59.1  cluster_2.0.6       
## [10] annotate_1.57.2      XML_3.98-1.10        AnnotationDbi_1.41.4
## [13] IRanges_2.13.28      S4Vectors_0.17.37    MSnbase_2.5.10      
## [16] ProtGenerics_1.11.0  BiocParallel_1.13.1  mzR_2.13.5          
## [19] Rcpp_0.12.16         Biobase_2.39.2       BiocGenerics_0.25.3 
## [22] xtable_1.8-2         knitr_1.20          

@@

##  [13] rsconnect_0.8.8       viridis_0.5.0         gdata_2.18.0         
##  [16] magrittr_1.5          memoise_1.1.0         doParallel_1.0.11    
##  [19] sfsmisc_1.1-2         limma_3.35.13         recipes_0.1.2        
##  [22] gower_0.1.2           rda_1.0.2-2           dimRed_0.1.0         
##  [25] lpSolve_5.6.13        prettyunits_1.0.2     colorspace_1.3-2     
##  [28] blob_1.1.0            dplyr_0.7.4           jsonlite_1.5         
##  [31] RCurl_1.95-4.10       hexbin_1.27.2         genefilter_1.61.1    
##  [34] bindr_0.1.1           impute_1.53.0         survival_2.41-3      
##  [37] iterators_1.0.9       glue_1.2.0            DRR_0.0.3            
##  [40] gtable_0.2.0          ipred_0.9-6           zlibbioc_1.25.0      
##  [43] kernlab_0.9-25        ddalpha_1.3.1.1       prabclus_2.2-6       
##  [46] DEoptimR_1.0-8        scales_0.5.0          vsn_3.47.1           
##  [49] mvtnorm_1.0-7         DBI_0.8               viridisLite_0.3.0    
##  [52] progress_1.1.2        foreign_0.8-70        bit_1.1-12           
##  [55] proxy_0.4-21          mclust_5.4            preprocessCore_1.41.0
##  [58] DT_0.4                lava_1.6              prodlim_1.6.1        
##  [61] sampling_2.8          htmlwidgets_1.0       httr_1.3.1           
##  [64] threejs_0.3.1         FNN_1.1               RColorBrewer_1.1-2   
##  [67] fpc_2.1-11            modeltools_0.2-21     pkgconfig_2.0.1      
##  [70] flexmix_2.3-14        nnet_7.3-12           caret_6.0-78         
##  [73] tidyselect_0.2.4      rlang_0.2.0           reshape2_1.4.3       
##  [76] munsell_0.4.3         mlbench_2.1-1         tools_3.5.0          
##  [79] RSQLite_2.0           pls_2.6-0             broom_0.4.3          
##  [82] evaluate_0.10.1       stringr_1.3.0         mzID_1.17.0          
##  [85] yaml_2.1.18           ModelMetrics_1.1.0    bit64_0.9-7          
##  [88] robustbase_0.92-8     randomForest_4.6-12   purrr_0.2.4          
##  [91] dendextend_1.7.0      bindrcpp_0.2          nlme_3.1-136         
##  [94] whisker_0.3-2         mime_0.5              RcppRoll_0.2.2       
##  [97] biomaRt_2.35.12       compiler_3.5.0        e1071_1.6-8          
## [100] affyio_1.49.1         tibble_1.4.2          stringi_1.1.7        
## [103] highr_0.6             lattice_0.20-35       trimcluster_0.1-2    
## [106] Matrix_1.2-12         psych_1.7.8           gbm_2.1.3            
## [109] pillar_1.2.1          MALDIquant_1.17       bitops_1.0-6         
## [112] httpuv_1.3.6.2        R6_2.2.2              pcaMethods_1.71.0    
## [115] affy_1.57.0           hwriter_1.3.2         codetools_0.2-15     
## [118] MASS_7.3-49           gtools_3.5.0          assertthat_0.2.0     
## [121] CVST_0.2-1            rprojroot_1.3-2       withr_2.1.2          
## [124] mnormt_1.5-5          diptest_0.75-7        grid_3.5.0           
## [127] rpart_4.1-13          timeDate_3043.102     tidyr_0.8.0          
## [130] class_7.3-14          rmarkdown_1.9         lubridate_1.7.3      
## [133] base64enc_0.1-3
